%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}

\cvsubsection{Academia and Education}

\cventry
    {Member} % Affiliation/role
    {\hrefs{https://fel.cvut.cz/en/faculty/faculty-structure/academic-senate}{Academic Senate of Faculty of Electrical Engineering, CTU}} % Organization/group
    {Prague} % Location
    {2019--2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Commision for the development of the faculty}
        \item {Work on the new election rules for the faculty that were implemented in 2021.}
      \end{cvitems}
    }

\cventry
    {Mentor} % Affiliation/role
    {\hrefs{https://www.technologicka-gramotnost.cz/olympiada}{Technologická olympiáda}} % Organization/group
    {Prague} % Location
    {2022, 2023, 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Technologická olympiáda is a czech national competion for highscool student teams.}
        \item {The teams should present novel solutions to one of the given problems.}
        \item {The mentor's role is to consult with the teams and give them feedback on their ideas and presentations.}
      \end{cvitems}
    }


\cvsubsection{Scout Movement}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Instructor} % Affiliation/role
    {\hrefs{https://hradek.skauting.cz/}{ČLK Hrádek: qualification course for young Scout leaders}} % Organization/group
    {Hrádek u Sušice, Pilsen, Online} % Location
    {2021--PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Instructor: methodology  (2022--PRESENT)}
        \item {Instructor: planning (2021)}
        \item {Adventure and experience: team leader (2021--2023), team member (PRESENT)}
        \item {Instructor: Scoutcraft (2023--PRESENT)}
      \end{cvitems}
    }

  %---------------------------------------------------------
    \cventry
      {Member} % Affiliation/role
      {\hrefs{https://krizovatka.skaut.cz/organizace/ustredni-organy/odbory-vykonne-rady/skautsky-odbor}{Department of Scouts and Guides}} % Organization/group
      {Prague, Online} % Location
      {2017--PRESENT} % Date(s)
      {
        \begin{cvitems} % Description(s) of experience/contributions/knowledge
          \item {Department of Scouts and Guides coordinates the education in the Czech Scout Association for older children (10--15 years old, all genders).} 
          \item {Main responsibility: team (patrol) system}
        \end{cvitems}
      }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Committee for the revision of the \emph{Skautská Stezka}} % Organization/group
    {Prague, Online} % Location
    {2013--2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Skautská Stezka is the main self-education material for children in the Czech Scout Association.} 
        \item {This committee was responsible for the last big revision of the material.}
        \item {The revision completely changed the structure and system, redesigned most of the activities and tasks and changed the design storyline of the material.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Deputy} % Affiliation/role
{\hrefs{http://stopaplzen.skauting.cz/}{Scout Group Stopa Plzeň}} % Organization/group
{Pilsen} % Location
{2013--2019} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {This group consists of five Scout units, approximately 400 members.} 
    \item {Main responsibilities of the group are coordination between units and organization of common events.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Leader} % Affiliation/role
{\hrefs{http://vlocka.skauting.cz/}{Scout Unit Vločka Plzeň}} % Organization/group
{Pilsen} % Location
{2009--2013} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {This group consists of children of all genders and age groups, approximately 100 members.} 
    \item {Currently, I prepare program for the unit only twice a year and I don't have any official position.}
  \end{cvitems}
}


\end{cventries}


%-------------------------------------------------------------------------------

\cvsubsection{Film Clubs}

\begin{cventries}
  \cventry
    {Organizer} % Affiliation/role
    {Six Feet Under Film Club} % Organization/group
    {Prague} % Location
    {2021--PRESENT} % Date(s)
    {}

  \cventry
    {Organizer} % Affiliation/role
    {Film Club of the Scout Institute in Prague} % Organization/group
    {Prague} % Location
    {2017--2018} % Date(s)
    {}

  \cventry
    {Organizer} % Affiliation/role
    {Pilsen Scout Film Club} % Organization/group
    {Pilsen} % Location
    {2013--2017} % Date(s)
    {}


\end{cventries}

