%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD Thesis project} % Position
    {Large-scale Mobility-on-demand: Simulation Studies and Optimization} % Project
    {CTU in Prague} % Location
    {ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {This thesis focuses on improving the large-scale Mobility-on-demand (MOD) systems.  
        Simulation studies are used to better understand MoD systems and answer related research questions. 
        Based on the insights gained from the simulations, we propose a new optimization method for optimal plan chaining.
        This new method has the potential to improve the efficiency of various MoD-related problems, which we demonstrate with the example of vehicle dispatching (Dial-a-ride problem).
        }
        \item {Currently, the thesis is submitted and waiting for defense. The last manuscript from the thesis focused on optimal plan chaining is in review in \emph{Transportation Research Part C: Emerging Technologies}.
        Finally, a subsequent manuscript focused on the plan chaining application is in review in \emph{Nature Computational Science}
        }
      \end{cvitems}
    }

    

%---------------------------------------------------------
  \cventry
    {Bell Textron Inc. Multi-Modal Traveler Modeling Project} % Position
    {
    \hrefs{https://www.aic.fel.cvut.cz/news/air-taxis-as-the-future-of-public-transport}{Feasibility of eVTOL Transport in Urban Environments}
    } % Project
    {CTU in Prague} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {This project studied the viability of using electric vertical take-off and landing travel system for urban mobility.}
        \item {Our transportation team defined the goals and requirements with Bell Textron Inc. and developed a simulation model to evaluate the feasibility of the eVTOL system.}
        \item I focused on the simulation model and optimal eVTOL station positioning.
        \item {We delivered the codebase and summarized our findings in a report.}
      \end{cvitems}
    }
\end{cventries}


% % %---------------------------------------------------------
