%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Fiedler, D}, Mrkos, J, 2023. Large-scale Ridesharing DARP Instances Based on Real Travel Demand. Presented at the 26th IEEE International Conference on Intelligent Transportation Systems (ITSC 2023). Preprint at \hrefs{https://arxiv.org/abs/2305.18859}{arXiv:2305.18859}}

    \cvpub{\textbf{Mrkos, J}, Basmadjian, R. 2022. Dynamic Pricing for Charging of EVs with Monte Carlo Tree Search. Smart Cities, 5(1): 223-240.}

    \cvpub{\textbf{Basmadjian, R}, Mrkos, J, Kirpes, B, Cuchý, M.  2020. A Reference Architecture for Interoperable Reservation Systems in Electric Vehicle Charging. Smart Cities, 3(4): 1405-1428.}

    \cvpub{\textbf{Schaefer, M}, Čáp, M, Mrkos, J, Vokřínek, J.  2019. Routing a Fleet of Automated Vehicles in a Capacitated Transportation Network. 2019 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 8223-8229.}

    \cvpub{\textbf{Basmadjian, R}, Kirpes, B, Mrkos, J, Cuchý, M.  2019. An Interoperable Reservation System for Public Electric Vehicle Charging Stations: A Case Study in Germany. Proceedings of the 1st ACM International Workshop on Technology Enablers and Innovative Applications for Smart Cities and Communities (TESCA'19), 22-29.}

    \cvpub{\textbf{Mrkos, J}, Komenda, A, Jakob, M.  2018. Revenue Maximization for Electric Vehicle Charging Service Providers Using Sequential Dynamic Pricing. Proc. of the 17th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2018), 832-840.}

    \cvpub{\textbf{Mrkos, J}, Komenda, A, Jakob, M.  2018. Dynamic Pricing Strategy for Electromobility using Markov Decision Processes. Proc. of the 10th International Conference on Agents and Artificial Intelligence (ICAART 2018), 507-514.}

    \cvpub{\textbf{Egan, M}, Drchal, J, Mrkos, J, Jakob, M.  2018. Towards Data-Driven On-Demand Transport. EAI Endorsed Transactions on Industrial Networks and Intelligent Systems, 5(14).}
\end{cvpubs}


% %---------------------------------------------------------
\cvsubsection{Accepted}
% %---------------------------------------------------------

\begin{cvpubs}

\cvpub{\textbf{Cuchý, M}, Jakob, M, Mrkos, J. 2024. Route and Charging Planning for Electric Vehicles: A Multi-Objective Approach. Transportation Letters.}

\end{cvpubs}

% %---------------------------------------------------------
\cvsubsection{In Review}
% %---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Fiedler, D}, Difonzo, F, Mrkos, J. 2024. Optimal Chaining of Vehicle Plans with Time Windows. In review at "Transportation Research Part C: Emerging Technologies". Preprint at \hrefs{http://arxiv.org/abs/2401.02873}{arXiv:2401.02873}}
\end{cvpubs}

% % %---------------------------------------------------------
