%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Software}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Maintainer, main contributor} % Role
    {\hrefs{https://github.com/aicenter/simod}{SiMoD}} % Project Name
    {Java, Python} % Language
    {2016-PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Simulation of Mobility-on-Demand Systems (SiMoD) is a software tool for simulating the operation of mobility-on-demand systems.}
        \item {The tool consists of an event-based simulation in Java and supporting Python scripts for input, output, and analysis.}
        \item {The simulation contains implementations of various algorithms for dispatching, rebalancing. There is also a station positioning algorithm in the Python part.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Maintainer, main contributor} % Role
{\hrefs{https://github.com/aicenter/Ridesharing_DARP_instances}{DARP Instances}} % Project Name
{PostgreSQL, Python} % Language
{2023-PRESENT} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Instances for large-scale ridesharing (DARP) problems together with the code for generating them from open data.}
    \item {Instances combine data from OpenStreetMap, municipality data, and Uber Movement.}
    \item {Three areas are covered: New York City, Chicago, and Washington, D.C.}
  \end{cvitems}
}    

%---------------------------------------------------------
\cventry
{Maintainer, contributor} % Role
{\hrefs{https://github.com/aicenter/shortest-distances}{Shortest Distances}} % Project Name
{C++} % Language
{2019-PRESENT} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Tool and library for fast computation of shortest distances in road networks.}
    \item {Various methods and datastructures are implemented with different trade-offs between memory usage and speed.}
    \item {The tool consists of a preprocesor for creating the datastructures and a query tool for computing the distances.}
    \item {There is a Java binding for the library.}
  \end{cvitems}
}   

%---------------------------------------------------------
\cventry
{Maintainer, contributor} % Role
{\hrefs{https://github.com/aicenter/agentpolis}{Agentpolis}} % Project Name
{Java, Python} % Language
{2016-PRESENT} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Event-based transportation simulation framework.}
    \item {Main dependency of SiMoD and similar projects}
    \item {Versatile and highly configurable.}
  \end{cvitems}
}   

%---------------------------------------------------------
\cventry
{Maintainer, main contributor} % Role
{\hrefs{https://github.com/F-I-D-O/info-maven-plugin}{Info plugin for Maven}} % Project Name
{Java} % Language
{2024-PRESENT} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Maven plugin for listing dependencies cached in the local repository.}
    \item {Available at Maven Central.}
  \end{cvitems}
}   


\end{cventries}
